Bayesian_portfolio_modeling

### 2016-06-15 portfolio/analysis/4b-Bayesian_portfolio_modeling.Rmd
fixes
I modified the code to allow the 4 arrays of ints to still be an array
with 1 random effect. Previously, a dimension error was being thrown by
STAN.

N = dim(testData)[1]
b1_cov = cbind(SPEC_DIV, DAYS) # fixed effect covariate on slope
sigma1_cov = cbind(SPEC_DIV, DAYS) # fixed effect covariate on slope
b1_cov_re = cbind(SPEC_DIV)
sigma1_cov_re = cbind(SPEC_DIV)

b0_re = cbind(P_HOLDER, PERMIT, PERMIT_AREA, PERMIT_SPEC)
b0_re_levels = apply(b0_re,2,max)
b0_re_n = dim(b0_re)[2]

b1_re = cbind(PERMIT, PERMIT_AREA, PERMIT_SPEC)
b1_re_levels = apply(b1_re,2,max)
b1_re_n = dim(b1_re)[2]

sigma0_re = cbind(P_HOLDER, PERMIT, PERMIT_AREA, PERMIT_SPEC)
sigma0_re_levels = apply(b0_re,2,max)
sigma0_re_n = dim(sigma0_re)[2]

sigma1_re = cbind(PERMIT, PERMIT_AREA, PERMIT_SPEC)
sigma1_re_levels = apply(sigma1_re,2,max)
sigma1_re_n = dim(sigma1_re)[2]

@@

### Center all of the covariate matrices
b1_cov = scale(b1_cov, scale=FALSE)
sigma1_cov = scale(sigma1_cov, scale=FALSE)
b1_cov_re = scale(b1_cov_re, scale=FALSE)
sigma1_cov_re = scale(sigma1_cov_re, scale=FALSE)
```

```{r}
# Named list of data
list_data = list("N"=N, "K_mean"=K_mean, "b1_cov"=b1_cov, "sigma1_cov"=sigma1_cov,
  "K_mean_re"=K_mean_re, "K_sig_re"=K_sig_re,"b1_cov_re"=b1_cov_re, "sigma1_cov_re"=sigma1_cov_re,
  "b0_re"=b0_re, "b0_re_levels"=b0_re_levels, "b0_re_n"=b0_re_n,
  "b1_re"=b1_re, "b1_re_levels"=b1_re_levels, "b1_re_n"=b1_re_n,
  "sigma0_re"=sigma0_re, "sigma0_re_levels"=sigma0_re_levels, "sigma0_re_n"=sigma0_re_n,
  "sigma1_re"=sigma1_re, "sigma1_re_levels"=sigma1_re_levels, "sigma1_re_n"=sigma1_re_n, "K_sig"=K_sig, "y"=y)
# parameters to monitor
list_pars = c("b0_mu","b0_dev","b0_tau", "b1_mu","b1_dev","b1_tau", "sigma0_mu","sigma0_dev","sigma0_tau", "sigma1_mu","sigma1_dev","sigma1_tau")

@@

stanMod = stan(file = 'portfolio_mixedModel.stan',data = list_data, 
  verbose = TRUE, chains = 4, thin = 1, warmup = 500, iter = 1000, 
  pars = list_pars)
p = extract(stanMod, list_pars, permuted=TRUE)
```

>>>>

N = dim(testData)[1]
b1_cov = cbind(SPEC_DIV) # fixed effect covariate on slope
sigma1_cov = cbind(SPEC_DIV) # fixed effect covariate on slope
b1_cov_re = cbind(SPEC_DIV)
sigma1_cov_re = cbind(SPEC_DIV)

b0_re = cbind(PERMIT) #cbind(P_HOLDER, PERMIT, PERMIT_AREA, PERMIT_SPEC)
b0_re_levels = apply(b0_re,2,max)
b0_re_n = dim(b0_re)[2]

b1_re = cbind(PERMIT)#cbind(P_HOLDER, PERMIT, PERMIT_AREA, PERMIT_SPEC)
b1_re_levels = apply(b1_re,2,max)
b1_re_n = dim(b1_re)[2]

sigma0_re = cbind(PERMIT)
sigma0_re_levels = apply(sigma0_re,2,max)
sigma0_re_n = dim(sigma0_re)[2]

sigma1_re = cbind(PERMIT)
sigma1_re_levels = apply(sigma1_re,2,max)
sigma1_re_n = dim(sigma1_re)[2]

@@

### Center all of the covariate matrices
#b1_cov = scale(b1_cov, scale=FALSE)
#sigma1_cov = scale(sigma1_cov, scale=FALSE)
#b1_cov_re = scale(b1_cov_re, scale=FALSE)
#sigma1_cov_re = scale(sigma1_cov_re, scale=FALSE)
```

```{r}
# Named list of data
list_data = list("N"=N, "K_mean"=K_mean, "b1_cov"=b1_cov, "sigma1_cov"=sigma1_cov,
  "K_mean_re"=K_mean_re, "K_sig_re"=K_sig_re,"b1_cov_re"=b1_cov_re, "sigma1_cov_re"=sigma1_cov_re,
  "b0_re"=b0_re, "b0_re_levels"=c(b0_re_levels,0), "b0_re_n"=b0_re_n,
  "b1_re"=b1_re, "b1_re_levels"=c(b1_re_levels,0), "b1_re_n"=b1_re_n,
  "sigma0_re"=sigma0_re, "sigma0_re_levels"=c(sigma0_re_levels,0), "sigma0_re_n"=sigma0_re_n,
  "sigma1_re"=sigma1_re, "sigma1_re_levels"=c(sigma1_re_levels,0), "sigma1_re_n"=sigma1_re_n, "K_sig"=K_sig, "y"=y)
# parameters to monitor
list_pars = c("b0_mu","b0_dev","b0_tau", "b1_mu","b1_dev","b1_tau", "sigma0_mu","sigma0_dev","sigma0_tau", "sigma1_mu","sigma1_dev","sigma1_tau")

@@

stanMod = stan(file = 'portfolio_mixedModel.stan',data = list_data, 
  verbose = TRUE, chains = 1, thin = 1, warmup = 20, iter = 50, 
  pars = list_pars)
p = extract(stanMod, list_pars, permuted=TRUE)
```
